### 2013-06-13 Tex/chapters/model.tex
fehlende Leerzeichen ergänzt

\subsection{Model}
\label{ssec:isingmodel}
    The used model is a modified 2D Ising model where the \(N\)sites are
    displaced nodes of a square lattice of edgelength \(L\) with
    periodic boundary conditions. The displacement is randomly gauss
    distributed with the standard deviation \(\sigma\). This \(\sigma\)
    is also called \emph{disturbance paramter} in the following.
    The hamiltonian of the Ising model is
    \(\hat{H} = \sum_{\avg{i,j}}J_{ij}s_{i}s_{j}\)
    where \(\avg{i,j}\) refers to by edges connected nodes.
    The edges are constructed according to the in section
    \ref{sec:graphtypes} defined rules. So that the lattice resembles a
    proximity graph. Each node \(i\) has a spin \(s_i = \pm 1\). Each
    edge has a weight \(J_{ij} = \exp (\alpha (1-d_{ij}))\) with the
    distance \(d_{ij}\) between the nodes \(i\) and \(j\). \(J\) is
    called \emph{coupling constant}.\\
    For \(\sigma = 0\) this is the standard Ising model with \(J = 1\),
    for which exists an analytical solution \cite{Onsager1944}.\\

>>>>

\subsection{Model}
\label{ssec:isingmodel}
    The used model is a modified 2D Ising model where the \(N\) sites
    are displaced nodes of a square lattice of edge length \(L\) with
    periodic boundary conditions. The displacement is randomly gauss
    distributed with the standard deviation \(\sigma\). This \(\sigma\)
    is also called \emph{disturbance paramter} in the following.
    The hamiltonian of the Ising model is
    \(\hat{H} = \sum_{\avg{i,j}}J_{ij}s_{i}s_{j}\)
    where \(\avg{i,j}\) refers to by edges connected nodes.
    The edges are constructed according to the in section
    \ref{sec:graphtypes} defined rules. So that the lattice resembles a
    proximity graph. Each node \(i\) has a spin \(s_i = \pm 1\). Each
    edge has a weight \(J_{ij} = \exp (\alpha (1-d_{ij}))\) with the
    distance \(d_{ij}\) between the nodes \(i\) and \(j\). \(J\) is
    called \emph{coupling constant}.\\
    For \(\sigma = 0\) this is the standard Ising model with \(J = 1\),
    for which exists an analytical solution \cite{Onsager1944}.\\
